Best practices for forecasting changes in biodiversity: an example using breeding birds

### 2017-09-03 manuscript/draft.Rmd
update figure captions

![**A.** Model predictions for [[STATE]] route [[ROUTE NUMBER]] when all
observers are treated the same (black points). **B.** Model predictions for the
same route when accounting for systematic differences between observers
(represented by the points' colors). In this example most models are made more
robust to observer turnover. Note that the "naive" model is less sensitive to
observer turnover, and does not benefit as much from modeling
it.](../figures/observer_predictions.png)

@@

Accounting for differences among observers generally improved measures of model
fit (Figure 7). Improvements primarily resulted from a small number of forecasts
where observer turnover caused a large shift in the reported richness
values. The naive baseline was less sensitive to these shifts, because it
largely ignored the richness values reported by observers that had retired by
the end of the training period (Figure 1). The average model, which gave equal
weight to observations from the whole training period, showed a larger decline
in performance when not accounting for observer effects -- especially in terms
of coverage. The performance of the mistnet JSDM was notable here, because its
prediction intervals retained good coverage even when not correcting for
observer differences, which we attribute to the JSDM's ability to model this
variation with its latent variables.

![Accounting for differences between observers typically has a small impact on
accuracy (especially for the "naive" model), but occasonally changes a
prediction's accuracy by more than 10 species. As a result the inclusion of
observer effects results in average improvements in overall model
fit.](../figures/observers.png)

>>>>

![**A.** Model predictions for route 72035 when all observers are treated the
same (black points). **B.** Model predictions for the same route when accounting
for systematic differences between observers (represented by the points'
colors). In this example most models are made more robust to observer turnover.
Note that the "naive" model is less sensitive to observer turnover, and does not
benefit as much from modeling it.](../figures/observer_predictions.png)

@@

Accounting for differences among observers generally improved measures of model
fit (Figure 7). Improvements primarily resulted from a small number of forecasts
where observer turnover caused a large shift in the reported richness values
(Appendix [[Figure Number]]). The naive baseline was less sensitive to these
shifts, because it largely ignored the richness values reported by observers
that had retired by the end of the training period (Figure 1). The average
model, which gave equal weight to observations from the whole training period,
showed a larger decline in performance when not accounting for observer effects
-- especially in terms of coverage. The performance of the mistnet JSDM was
notable here, because its prediction intervals retained good coverage even when
not correcting for observer differences, which we attribute to the JSDM's
ability to model this variation with its latent variables.

![Controlling for differences among observers generally improved each model's
predictions, on average. The magnitude of this effect was negligible for the
Naive baseline, however.](../figures/obs_arrows.png)
